---
title: "Exercises"
author: Research with Computational Biology (ReComBio)
date: August 26, 2024
output: html_document
---

\

# Part 1: Introduction to R and the R Syntax

\

\

## Chapter 3: Data visualization

\

\

#### Load libraries

\


```{r, message=F, warning=F}
library(ggplot2)
library(maditr)
library(dplyr)
```

\

\

#### Load dataframe

\

```{r}
r2_gse62564_GSVA_Metadata <- readRDS("../../ReComBio Scientific/ReComBio Book English/recombio bookdown/data/r2_gse62564_GSVA_Metadata.rds")
```

\

\

#### Make Variables of Numeric Type

\

```{r make numeric}
r2_gse62564_GSVA_Metadata <- r2_gse62564_GSVA_Metadata %>% 
   mutate_at("HALLMARK_HYPOXIA", as.numeric) %>%
   mutate_at("HALLMARK_INFLAMMATORY_RESPONSE", as.numeric) %>%
   mutate_at("ADRN_Norm_vs_Hypo_Up_554.txt", as.numeric) %>%
   mutate_at("ADRN_Norm_vs_Hypo_Down_635.txt", as.numeric)
```


\

\

\

## Question 1

\

Use R plot functions to visualize the correlation between Hallmark Hypoxia and Hallmark Inflammatory Response

\

#### Solution:

HALLMARK_INFLAMMATORY_RESPONSE vs. HALLMARK_HYPOXIA

```{r, warning=F, message=F}
qplot(HALLMARK_INFLAMMATORY_RESPONSE, HALLMARK_HYPOXIA, 
      data = r2_gse62564_GSVA_Metadata,
      #colour=quantile,
      ylab = "HALLMARK_HYPOXIA",
      xlab = "HALLMARK_INFLAMMATORY_RESPONSE")
```

\

\

\

## Question 2

\

Use R plot functions to visualize the correlation between Hallmark Hypoxia and Hallmark Inflammatory Response

\

#### Solution: 

HALLMARK_INFLAMMATORY_RESPONSE vs. ADRN_Norm_vs_Hypo_Up_554.txt

```{r}
qplot(HALLMARK_INFLAMMATORY_RESPONSE, ADRN_Norm_vs_Hypo_Up_554.txt, 
      data = r2_gse62564_GSVA_Metadata,
      # colour=quantile,
      xlab = "HALLMARK_INFLAMMATORY_RESPONSE",
      ylab = "ADRN_Norm_vs_Hypo_Up_554.txt")
```

\

\

\

## Question 3

\

Use R plot functions to visualize the correlation between Hallmark Hypoxia and Hallmark Inflammatory Response

\

#### Solution: 

HALLMARK_INFLAMMATORY_RESPONSE vs. ADRN_Norm_vs_Hypo_Down_635.txt

```{r HALLMARK_INFLAMMATORY_RESPONSE vs. ADRN_Norm_vs_Hypo_Down_635.txt}
qplot(HALLMARK_INFLAMMATORY_RESPONSE, ADRN_Norm_vs_Hypo_Down_635.txt, 
      data = r2_gse62564_GSVA_Metadata,
      # colour=quantile,
      ylab = "ADRN_Norm_vs_Hypo_Down_635.txt",
      xlab = "HALLMARK_INFLAMMATORY_RESPONSE")
```

\

\

\

## Question 4

\

From the analysis of questions 1-3, choose the correct option:

- [ ] HALLMARK_INFLAMMATORY_RESPONSE and HALLMARK_HYPOXIA have a positive correlation because hypoxia is always beneficial in the tumor microenvironment

- [ ] HALLMARK_INFLAMMATORY_RESPONSE and ADRN_Norm_vs_Hypo_Up_554.txt have a positive correlation because hypoxia upregulation in this case, is beneficial in the tumor microenvironment

- [ ] HALLMARK_INFLAMMATORY_RESPONSE and ADRN_Norm_vs_Hypo_Up_554.txt have a positive correlation because hypoxia upregulation has a negative impact on survival

- [ ] HALLMARK_INFLAMMATORY_RESPONSE and ADRN_Norm_vs_Hypo_Down_635.txt have a negative correlation because hypoxia upregulation in this case, is not beneficial in the tumor microenvironment

\

\

\

## Question 5

\

Which gene expression group has worse survival probability?

- [ ] High HIF1A expression
- [ ] Low HIF1A expression

\

\

\

## Question 6

\

Which phenotype score group has worse survival probability?

- [ ] High Hallmark Hypoxia
- [ ] Low Hallmark Hypoxia

\

\

\

## Question 7

\

Which phenotype score group has worse survival probability?

- [ ] High Hallmark Inflammatory Response
- [ ] Low Hallmark Inflammatory Response

\

\

\

## Question 8

\

Plot the survival curve of the MYCN status variable. Which MYCN status has worse survival outcome? 

- [ ] Individuals with MYCN amplification
- [ ] Individuals without MYCN amplification
- [ ] The MYCN group with unknown MYCN status


\

\

\

## Question 9

\

Plot the survival curve of the INSS stage variable. Which INSS stage has worse survival outcome? 

- [ ] INSS Stage I
- [ ] INSS Stage II
- [ ] INSS Stage III
- [ ] INSS Stage IV
- [ ] INSS Stage IV A


\

\

\

## Question 10

\

Mark TRUE or FALSE.

- [ ] The higher the age at diagnosis the greater the HIF1A expression difference between HR and non-HR
- [ ] The lower the age at diagnosis the greater the HIF1A expression difference between HR and non-HR



\

\

\

# Part 2: Machine Learning

\

\

## Chapter 1: Classification

\

\

## P2 Question 1

\

How can you predict what label a new patient will have using the logistic regression model constructed in R? 

\

- [ ]  I can build a vector to provide as input to R so that the model can use the parameters it calculated to make the prediction

- [ ]  If I have more than 2 patients to predict, I can build a dataframe to input to R

- [ ]  It is not possible to know if a patient has high risk neuroblastoma disease without doing a FISH (Fluorescence *in situ* hybridization) and understanding if the person has MYCN amplification

\

\

\

## P2 Question 2

\

How can you know if a model represents a good indicator for the high risk status of a patient? 

\

- [ ]  If the model has high accuracy

- [ ]  If the model has medium accuracy

- [ ]  If the model has low accuracy

\

\

\


## P2 Question 3

\

Write a command to input information about the predictor variables of a patient into R. In order to force your brain to come up with a solution, please discuss the strategy to solve this problem in groups.


\

\

\

## P2 Question 4

\

Write a command to predict the high risk label for the patient based in the patient's gene expression pattern. In order to force your brain to come up with a solution, please discuss the strategy to solve this problem in groups.


\

\

\



